Kinematics of the Palomar 5 stellar stream from RR Lyrae stars

### 2019-10-01 paper/main.tex
gray
Updates from Overleaf

We also detect a distance trend from the closer leading tail ($d \approx 19.4~\kpc$ at $\phi_1 \approx 5\degr$) to the more distant trailing tail ($d \approx 21.3~\kpc$ at $\phi_1 \approx -5\degr$).
While the proper motion in right ascension appears consistent with constant or only a mild gradient over the extent of the stream, we see a significant gradient in the declination component, with a difference of about $\approx 1~\masyr$ from trailing to leading tail.
% \sa{worth mentioning Pearson 2017, fig 2 where this same trend is also seen (flatter gradient in RA proper motion than in dec proper motion?}
% APW: What were mu_1 and mu_2? Were those proper motions in RA/Dec?

@@

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{rrls_PA.pdf}
\caption{Amplitude ($g$-band) versus Period for RRLs in the Pal~5 field membership probabilities $>0.1$ (small markers) inside the Pal~5 track (large markers), colored by membership probability. The distribution of the RRLs found in the cluster and its tails is consistent with an Oosterhoff type I (dashed line). }
\label{fig:PA_diagram}
\end{center}
\end{figure*}

>>>>

We also detect a distance trend from the closer leading tail \changes{($d \approx 19.4~\kpc$ and $\approx$$18~\kpc$ at $\phi_1 \approx 5\degr$ and $10\degr$, respectively) to the more distant trailing tail ($d \approx 21.3~\kpc$ and $\approx$$21.9~\kpc$ at $\phi_1 \approx -5\degr$ and $-10\degr$, respectively)}.
While the proper motion in right ascension appears consistent with constant or only a mild gradient over the extent of the stream, we see a significant gradient in the declination component, with a difference of about $\approx 1~\masyr$ from trailing to leading tail.
% \sa{worth mentioning Pearson 2017, fig 2 where this same trend is also seen (flatter gradient in RA proper motion than in dec proper motion?}
% APW: What were mu_1 and mu_2? Were those proper motions in RA/Dec?

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=0.85\textwidth]{rrls_PA.pdf} 
\caption{Amplitude ($g$-band) versus Period for all RRLs in the Pal~5 field. \changes{Stars with membership probabilities $>0.1$ are colored by membership probability, with those inside the Pal~5 track shown with large (star) markers. RRLs with membership probabilities $<0.1$ are shown as gray markers.} The distribution of the RRLs found in the cluster and its tails is consistent with an Oosterhoff type I (dashed line). }
\label{fig:PA_diagram}
\end{center}
\end{figure*}

@@
